\documentclass[a4paper,11pt]{article}
\usepackage[colorlinks,linkcolor=blue]{hyperref}
\title{35763432 Peer Review}
\begin{document}

\maketitle

One thing I would like to note before proceeding to make suggestions on your paper is that I realized after reading your essay that my level of expertise is not really sufficient to make an opinion. The paper is logical, the modeling process is logical, the language is well presented, and the problem is analyzed in detail using a more responsible model and summarized at a high level. The following suggestions are just my humble opinion, and you do not have to correct them if you feel they are biased.

Firstly, I looked up the Harvard format citation in Lancaster University's bibliographic citation rules, and it appears that the school requires that the text be marked by author and year rather than number, please see \href{https://lancaster.libguides.com/harvard/in-text}{Lancaster Harvard In Text} for details. However, it looks like the numbers are in a more intuitive format. I am hesitant on this point as well.

Secondly, I would like to enquire that are the references to the R language itself appropriate? In other words, you reference the R language itself, to a large extent, you might also reference the R package you are calling, vice versa. I have my doubts about this question, as well as in my article I cite all the tools I use. However, I am not sure if this is necessary. Alex explained that it depends on the standard of review in class, but that is not a good judgement in this project. Therefore, I reckon that this needs to be checked with Alex.


Finally, could you please add the values of AIC or BIC that you got in your model, likewise this is not necessary certainly. However I am curious about this value since you did a stepwise regression on the model to select the final model. These two values are common targets for stepwise regression.

In conclusion, this is an extremely mature paper, and making suggestions is nitpicking in a way. In my understanding, these three points do not affect the overall completion of the paper, but are only suggestions from my personal thinking point of view. I need to learn from you in terms of completeness of the logical chain and fluency of the language, and thank you for bringing me the paper of very high standard for my study and reference!

\end{document}