\documentclass[a4paper,11pt]{article}
\usepackage[colorlinks,linkcolor=blue]{hyperref}
\title{35746973 Peer Review}
\begin{document}

\maketitle

This article is logical, clearly structured, analytically sound, and fluent in language. By and large, I cannot disagree with anything. Overall, I can only analyze this paper from the perspective of writing my own paper, but that doesn't guarantee that my suggestions are all reasonable. If you feel that the following three suggestions do not apply to your essay, please analyze it from your own perspective.

Firstly, it seems to me that the line spacing in your article is not 1.5 times as long. I used the word adjustment 1.5x and then compared it to your article and found that the 5 assumptions you may have listed in the Proposal/Methods section were not adjusted to 1.5x line spacing. It is also possible that I am misunderstanding since I did not use an unordered list for presentation in my own paper.

Secondly, if it is convenient for you, could you demonstrate the p-value of the estimated coefficient? In my personal analysis, I tend to look at the coefficients directly to determine if they are significant or not, as this gives a more intuitive analysis of how accurate the model is. Of course, due to space constraints, it's fine to write without being significant.

Finally, is it necessary to mention ISSN and dio in references? I looked up the Harvard format citation in Lancaster University's bibliographic citation rules, and it appears that the proposal format provided by the school does not contain both of these pieces of information, please see \href{https://lancaster.libguides.com/harvard/in-text}{Lancaster Harvard In Text} for details. As this is also my first time using the Harvard format, I am not really sure if I need to include both data, so if you think this suggestion is unreasonable, please keep them.

In summary, I really think your paper is very well written. These suggestions are just my personal opinion to some extent, and you do not have to adopt them completely if you think they do not quite fit the style of your paper. And thank you for writing such an excellent paper for me to study!

\end{document}
